(tentative) Rotational Spectral Unmixing of Exoplanets

### 2016-11-21 paper/main.tex
trying different regularization terms

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$.The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$. The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 11 times in one rotation. \color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$ \color{red} when the lightcurves are sampled 11 times in one rotation. \color{black}. The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 11 times in one rotation. \color{black} The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 15 times in one rotation. \color{black}. The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation. \color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}. In the regularization term, not $f_{lk}$ but $(f_{lk}-f_{k}^{\rm (ave)})/f_{k}^{\rm (ave)}$ are used where $f_{k}^{\rm (ave)} = (\sum_l f_{lk})/L$. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation. \color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}. In the regularization term, not $f_{lk}$ but $g_{lk}$ are used. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
